### 2017-05-23 sheets/basis-2/sheet-basis-2.tex
Fixed part of Mostafa's solutions.

\begin{answer}
\begin{enumerate}
\item
\begin{itemize}
\item Since every set is mapped to another set (its powerset), then all objects are mapped.
\item A function $f: X \rightarrow Y$ is mapped to $F: P(X) \rightarrow P(Y)$, such that $F(x)  = \{x \in X\}$.
\item This makes the axioms follow easily from composition in $\mathbf {Set}$. Therefore, it satisfies functor laws.
\item It is faithful (A set has only one powerset) and not full (consider a function that takes the entire powerset as an element and maps it to the other powerset).
\end{itemize}
\item
The only difference is mapping elements in the powerset to their preimage set. The rest of the argument is the same.
\end{enumerate}
\end{answer}

\begin{exercise}
  Let $A$ and $B$ be posets, and $\A$ and $\B$ be the corresponding categories. Consider a contravariant functor $F:\A^{\op}\rightarrow \B$. Describe properties of the corresponding function $f:A\rightarrow B$.
\end{exercise}

\begin{answer}
  For every arrow $x \to y$ in $\A$, there is an arrow $f : y \to x$ in $\A^\op$ and hence an arrow $F(f) : F(y) \to F(x)$ in $\B$.
  In the language of posets this means that $x \leq y$ implies $f(x) \geq f(y)$, i.e.\ $f$ is monotonically decreasing.
  The functor laws hold tautologically in posets and don't tell us anything about $f$.
\end{answer}

>>>>

\begin{answer}
\begin{enumerate}
   \item
   \begin{itemize}
   \item Since every set is mapped to another set (its powerset), then all objects are mapped.
   \item A function $f: X \rightarrow Y$ is mapped to $F: P(X) \rightarrow P(Y)$, such that $F(x)  = \{f(x) | x \in X\}$.
   \item This makes the axioms follow easily from composition in $\mathbf {Set}$:
   \begin{itemize}
   \item $F(f'\of f) (a) = F(f' \of f(a)) = F(f'(f(a)))$
   \item $F(f') \of F(f) (a) = F(f') \of F(f(a)) = F(f'(f(a)))$
   \item $F(f' \of f) = F(f') \of F(f)$
   \item Identity law can be verified easily
   \item Therefore, it satisfies functor laws and it is a functor.
   \end{itemize}
   \item It is faithful (A set has only one powerset) and not full (consider a function that takes the entire powerset as an element and maps it to the other powerset).
   \end{itemize}
   \item
   The only difference is mapping elements in the powerset to their preimage set. The rest of the argument is the same.
\end{enumerate}
\end{answer}
